Pool Model Paper

### 2023-08-24 pool_model.tex
Add System/ODEs/Parameters  for the ABM.

\cmtb{We can take some toy model (e.g the one from group seminar) and do agent-based simulation. (add spatial component)
Then from this simulation we sum bacteria and get growth curves.
And using our model equations we get also growth curves.
And find prob diffusion coef, maybe rates where model works fine.
For sim maybe we will need to name specific bacteria species. (maybe nicer)}

>>>>

To test the spatial limitations of the described above approach consider the system consisting from two bacterial species thet can be described bt two internal states: lag and growth states. 
Both of these species grow using limiting resource pool $R$ with different growth constants $\alpha$ and different lengths of lag phase determined by parameter $\lambda$.
Moreover, the species 1 is able to release a certain antimicrobial component $I$ that shows inhibitory effect on species 2.
The ODEs the bacterial population can be written as: 
\begin{equation}
    \begin{cases}
        \dot{L_1} = -\lambda_1 R L_1\\
        \dot{G_1} = \lambda_1 R L_1 + \alpha_1 R G_1\\
        \dot{L_2} = -\lambda_2 R L_2\\
        \dot{G_2} = \lambda_2 R L_2 + \frac{\alpha_2}{1 + \mu_I I} R G_2\\
    \end{cases}.
    \label{eq:spatial_limit_F}
\end{equation}

The microenvironment of our system contains the resource and the inhibitor molecules:
\begin{equation}
    \begin{cases}
        \dot{R} = -\frac{\alpha_1}{N_t} R G_1-\frac{\alpha_2}{N_t} R G_2 \\
        \dot{I} = \kappa G_1
    \end{cases}.
    \label{eq:spatial_limit_H}
\end{equation}

\begin{table}[H]
    \centering
    \begin{tabular}{ccc}
    \specialrule{.1em}{.01em}{.05em} 
    \textbf{Parameter} \hspace{3mm} & \textbf{Value} \hspace{3mm} & \textbf{Units}\\
    \toprule
    $\lambda_1$ & 0.008  & [time$^{-1}$]                 \\
    $\lambda_2$ & 0.005  & [time$^{-1}$]                 \\
    $\alpha_1$  & 4.0    & [time$^{-1}$]                 \\
    $\alpha_2$  & 5.0    & [time$^{-1}$]                 \\
    $\kappa$    & 0.1    & [(cell $\cdot$ time)$^{-1}$]  \\
    $\mu_I$     & 0.1    & [cell$^{-1}$]                 \\
    $N_t$       & $10^4$ & [cell]                        \\
    \bottomrule
    \end{tabular}
    \caption{{\footnotesize The list of the parameters of the system.}}
    \label{tab:spatial_limit_param}
\end{table}

\begin{table}[H]
    \centering
    \begin{tabular}{ccc}
    \specialrule{.1em}{.01em}{.05em} 
    \textbf{Variable} \hspace{3mm} & \textbf{Initial Value} \hspace{3mm} & \textbf{Units}\\
    \toprule
    $L_1$ & 5.0 & [cell]        \\
    $G_1$ & 0.0 & [cell]        \\
    $L_2$ & 5.0 & [cell]        \\
    $G_2$ & 0.0 & [cell]        \\
    $R$   & 1.0 & [cell/cell]   \\
    $I$   & 0.0 & [cell]        \\
    \bottomrule
    \end{tabular}
    \caption{{\footnotesize The list of the initial values of the system.}}
    \label{tab:spatial_limit_init}
\end{table}

\begin{figure}[H]
    \begin{center}
    \includegraphics[width=0.67\textwidth]{Figures/pool_model_spatial.pdf}
    \caption{{\footnotesize The output of the model (\ref{eq:spatial_limit_F}, \ref{eq:spatial_limit_H}) for given parameters and initial valued presented in Tables \ref{tab:spatial_limit_param}, \ref{tab:spatial_limit_init}, respectively.
    The observables of the system are the bacterial count of each species $L+G$ (blue and orange lines) and the total bacterial count of the system (green).}}
    \label{fig:spatial_limit_plot1}
    \end{center}
\end{figure}

\cmtb{The ABM additional parameters $D_R$, $D_I$, $q$ (At which level of $R_i$ cell division happens) and more parameters describing bacterial division.}
